r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2021-01-18 r-package/paper2020/paper2020.Rmd
paper, edits to text and plot

ggplot(data=plot_data, aes(y = travel_time, x = reorder(fromId, mediantt))) +
  geom_point(alpha = 0.1, size = .7) +
  geom_line(aes(y=mediantt, group=toId), color="#FE9F45", size=1.5) +
  expand_limits(y = 120) +
  scale_y_continuous(breaks = c(0, 30, 60, 90, 120)) +
  theme_minimal() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.x = element_blank(), 
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(fill = NA, colour = "grey80", size=1)) +
  labs(title = "Travel time uncertainty per destination",
       y = "Travel Time (min)", x='Destinations')
```

@@

ggplot(na.omit(travel_times.interp)) +
  geom_contour_filled(aes(x=x, y=y, z=travel_time)) +
  geom_sf(data = street_net$edges, color = "gray55", size=0.1, alpha = 0.7) +
  coord_sf() +
  labs(fill = "cutoff") +
  theme_minimal() +
  theme(axis.title = element_blank())

>>>>

ggplot(data=plot_data, aes(y = travel_time, x = reorder(fromId, mediantt))) +
  geom_point(alpha = 0.3, size = .7) +
  geom_line(aes(y=mediantt, group=toId), color="#FE9F45", size=1.5) +
  expand_limits(y = 120) +
  scale_y_continuous(breaks = c(0, 30, 60, 90, 120)) +
  theme_minimal() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(fill = NA, colour = "grey80", size=1)) +
  labs(title = "Travel time uncertainty per destination",
       y = "Travel Time (min)", x='Destinations ordered by median travel time')
```

@@

ggplot(na.omit(travel_times.interp)) +
  geom_contour_filled(aes(x=x, y=y, z=travel_time), alpha=.7) +
  geom_sf(data = street_net$edges, color = "gray55", size=0.1, alpha = 0.7) +
  scale_fill_viridis_d(direction = -1, option = 'B') +
  coord_sf() +
  labs(fill = "cutoff in minutes") +
  theme_minimal() +
  theme(axis.title = element_blank())
